Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-07-07 paper/main.tex
Joshua's remarks for section 3

In this article, we describe our system for a subset of Clight to
discuss general ideas instead of technical details.  This subset is
given by the following grammar.
%
\begin{align*}
S &:= \code{assert}~E
\mid \code{skip}
\mid \code{break}
\mid \code{return}~x
\mid x \gets E
\mid x \gets f(x^*)
\\
& \mid \code{loop}~S
\mid \code{if}(E)~S~\code{else}~S
\mid S;S
\mid \code{tick}(n)
\end{align*}
%
Expressions $E$ are left abstract in our presentation.  For our
analysis framework, it is only important that they are side-effect
free.
%
The most notable difference to full Clight is that we can only assign
to variables and thus do not consider operations that update the heap.
Moreover, function arguments and return values are assumed to be
variables.  In the implementation we can deal with heap updates and
general function calls and returns.  However, we have not implemented
function pointers, \code{goto} statements, \code{continue} statements,
and \code{switch} statements.

@@

A program state $\state = (\theta, \gamma)$ composed of two maps from
variable names to integers. The first map $\theta : \text{Locals} \to
\Z$ assigns integers to local variables of a function and the second
map $\gamma : \text{Globals} \to \Z$ gives values to global variables
of the program.  In this article, we assume that all values are
integers but in the implementation we support all data types of
Clight.
%
The evaluation function \evalE{\cdot}{} maps an expression $e \in
E$ to a value $\evalE{e}{\state} \in \Z$ in the program state
$\state$.

For simplicity, we assume that local variables and global variables
are always different.  We just write $\state(x)$ to obtain the value of
$x$ in program state $\state$. \iffull{Such a lookup is defined as
$$
(\theta, \gamma)(x) =
\left\{
\begin{array}{lr}
\theta(x) & \mbox{ if } x \in \dom \theta \\
\gamma(x) & \mbox{ if } x \in \dom \gamma
\end{array}
\right..
$$}{}
\iffull{For a program state $\state$, we}{We} similarly write $\state[x \mapsto v]$
for the program state that maps $x$ to $v$ and behaves as $\state$ for
all other variables, regardless whether $x \in \dom \theta$ or $x \in
\dom \gamma$.

The small-step semantics is standard, except that it tracks the
resource consumption of a program.  The semantics is oblivious to the
resource of interest for the user of our system.  We achieve this
independence by parameterizing evaluations with a resource
\emph{metric} $M$; a tuple of nine rational numbers, one map $M_e :
\text{Expr} \to \Q$ from expressions to rational numbers, and one map
$M_t : \Z \to \Q$ from integers to rational numbers.
$$
M = (
M_a,
M_b,
M_r,
M_u,
M_f,
M_l,
M_c^1,
M_c^2,
M_s,
M_e(E),
M_t(n)
)
$$
Each of these rational numbers indicates the amount of resource
consumed by a corresponding operation.  If the assigned resource cost
is negative then it means that resources are released.  The metric
that we use in the implementation can also depend on other information
that is statically available such as the name of the called function
or the number of arguments.

>>>>

In this article, we describe our system for a subset of Clight that is
sufficient to discuss the general ideas.  This subset is given by the
following grammar.
%
\begin{align*}
S &:= \code{assert}~E
\mid \code{skip}
\mid \code{break}
\mid \code{return}~x
\mid x \gets E
\mid x \gets f(x^*)
\\
& \mid \code{loop}~S
\mid \code{if}(E)~S~\code{else}~S
\mid S;S
\mid \code{tick}(n)
\end{align*}
%
Expressions $E$ are left abstract in our presentation.  For our
analysis framework, it is only important that they are side-effect
free.
%
The most notable difference to full Clight is that we can only assign
to variables and thus do not consider operations that update the heap.
Moreover, function arguments and return values are assumed to be
variables.  This is only for simplifying the presentation; in the
implementation we can deal with heap updates and general function
calls and returns.  However, we have not implemented our framework for function
pointers, \code{goto} statements, \code{continue} statements, and
\code{switch} statements.

@@

A program state $\state = (\theta, \gamma)$ composed of two maps from
variable names to integers. The first map, $\theta : \text{Locals} \to
\Z$, assigns integers to local variables of a function, and the second
map, $\gamma : \text{Globals} \to \Z$, gives values to global variables
of the program.  In this article, we assume that all values are
integers but in the implementation we support all data types of
Clight.
%
The evaluation function \evalE{\cdot}{} maps an expression $e \in
E$ to a value $\evalE{e}{\state} \in \Z$ in the program state
$\state$.

For simplicity, we assume that local variables and global variables
are always different.  We just write $\state(x)$ to obtain the value of
$x$ in program state $\state$. \iffull{Such a lookup is defined as
$$
(\theta, \gamma)(x) =
\left\{
\begin{array}{lr}
\theta(x) & \mbox{ if } x \in \dom \theta \\
\gamma(x) & \mbox{ if } x \in \dom \gamma
\end{array}
\right..
$$}{}
\iffull{For a program state $\state$, we}{Similarly} we write $\state[x \mapsto v]$
for the program state that maps $x$ to $v$ and behaves as $\state$ for
all other variables, regardless whether $x \in \dom \theta$ or $x \in
\dom \gamma$.

The small-step semantics is standard, except that it tracks the
resource consumption of a program.  The semantics is parametric in the
resource of interest for the user of our system.  We achieve this
independence by parameterizing evaluations with a resource
\emph{metric} $M$; a tuple of nine rational numbers, one map $M_e :
\text{Expr} \to \Q$ from expressions to rational numbers, and one map
$M_t : \Z \to \Q$ from integers to rational numbers
%
\iffull{.$$
M = (
M_a,
M_b,
M_r,
M_u,
M_f,
M_l,
M_c^1,
M_c^2,
M_s,
M_e(E),
M_t(n)
)
$$}{$M_a$, $M_b$, $M_r$, $\ldots\;$.

}
Each of these rational numbers indicates the amount of resource
consumed by a corresponding operation.  If the assigned resource cost
is negative then it means that resources are released.  The metric
that we use in the implementation can also depend on other information
that is statically available such as the name of the called function
or the number of arguments.
